\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,shadows}
\usepackage{mdframed}
\usepackage{enumitem}

\definecolor{lightgray}{rgb}{0.95,0.95,0.95}
\definecolor{darkgray}{rgb}{0.4,0.4,0.4}
\definecolor{editorGreen}{rgb}{0,0.5,0}

\lstset{
    backgroundcolor=\color{lightgray},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    commentstyle=\color{editorGreen},
    keepspaces=true,
    keywordstyle=\color{blue},
    numbers=left,
    numberstyle=\tiny\color{darkgray},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2,
    frame=single
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Shamagama (Yaksha FAQ Portal) Project Report},
    pdfpagemode=FullScreen,
}

\title{Shamagama (Yaksha FAQ Portal)\\ \large Crowd Sourcing FAQ Project Report}
\author{Team vicharanashala}
\date{June 2026}

\begin{document}

\maketitle

\begin{center}
    \textbf{Repository Name:} Shamagama (Yaksha FAQ Portal) \\
    \textbf{Repository Link:} \href{https://github.com/vicharanashala/crowd-source-faq}{github.com/vicharanashala/crowd-source-faq}
\end{center}

\newpage
\tableofcontents
\newpage

\section{Executive Summary}
Organizations running large-scale communities face an exponential growth of repetitive queries. Conventional FAQ systems are static, require extensive manual upkeep, and quickly become obsolete. 

\textbf{Shamagama} (internally designated as the \textbf{Yaksha FAQ Portal}) is an advanced, enterprise-ready FAQ management and community Q\&A platform engineered to serve up to 1 million registered users. It automates the FAQ lifecycle end-to-end to achieve a ``zero-human'' steady state. The platform combines hybrid vector search (local 768-dim embeddings merged via Reciprocal Rank Fusion) with automated Zoom ingestion, LLM-based FAQ auditing, reputation-based peer reviews, and gamified ticket prioritization (Golden Tickets).

\section{Introduction}
\subsection{Problem Statement}
Modern communities generate knowledge at a rapid rate, yet this knowledge remains siloed in Zoom meetings, chat logs, and forum threads. When users have questions, they ask queries that have been answered before, burdening administrators. Searching past recordings is tedious, and manual verification is slow. Over time, software updates or policy changes cause FAQs to ``drift'' and become inaccurate, with no automated tracking mechanism.

\subsection{The Shamagama Solution}
Shamagama provides a full-stack, AI-orchestrated community Q\&A portal centered around four automation pillars:
\begin{itemize}
    \item \textbf{Zero-Touch Ingestion:} Automatically extracts Q\&A pairs from Zoom transcripts.
    \item \textbf{Zero-Touch Answering:} Automatically answers community posts using hybrid search and context-guided LLM responses.
    \item \textbf{Zero-Touch Quality Control:} Periodically checks approved FAQs against newer ingestion inputs to flag outdated or contradictory answers.
    \item \textbf{Zero-Touch User Lifecycle:} Anonymizes user accounts upon request to comply with privacy regulations (GDPR) while keeping user contributions intact.
\end{itemize}

\section{System Design \& Architecture}
Shamagama employs a decoupled three-tier architecture: a React Single Page Application (SPA), an Express REST API, and a MongoDB Atlas database.

\subsection{Architectural Components}
\begin{enumerate}
    \item \textbf{Client Layer (React SPA):} Formed with React 18, TypeScript, Tailwind CSS, Framer Motion, and Axios.
    \item \textbf{API Middleware Gateway (Express):} Comprises rate limiting, security headers (Helmet), authentication verification (JWT), and request validation (Zod).
    \item \textbf{Service Controllers:} Organizes business logic including search, community posts, Zoom OAuth, and moderation.
    \item \textbf{Data \& Intelligence Layer:} MongoDB Atlas (Vector indexes), Upstash Redis (optional cache), Cloudinary, and local WebAssembly embeddings.
\end{enumerate}

\subsection{Database Schema Design}
The relational structure of key entities in Shamagama is summarized below:
\begin{description}
    \item[User:] Accounts, roles, Zoom OAuth tokens, Spurti Points balance ($sp$), and soft-delete flags.
    \item[FAQ:] Question, answer, 768-dim embedding array, freshness tier (evergreen/seasonal/volatile), and lastVerifiedDate.
    \item[CommunityPost:] Title, content, status, and an embedded array of comment sub-schemas to optimize read queries.
    \item[SupportRequest:] Dynamic context fields, troubleshooting status, and Golden Ticket flags.
\end{description}

\section{Implementation}
\subsection{Tech Stack \& Justification}
\begin{itemize}
    \item \textbf{MongoDB Atlas \& Mongoose:} Native Vector Search integration enables cosine-similarity vector queries directly in the primary database without requiring a separate vector database.
    \item \textbf{Express.js:} Fast, minimalist framework with excellent middleware support for security and authentication.
    \item \textbf{React 18 \& Vite:} Enables optimistic UI updates for nested comments and fast client routing.
    \item \textbf{Node.js (TypeScript ESM):} Guarantees type-safe operations across services and conforms to modern ES modules syntax.
\end{itemize}

\subsection{Module / Feature Breakdown}
\begin{description}
    \item[Vector Search Service:] Generates local 768-dim embeddings via \texttt{@xenova/transformers} (\texttt{multi-qa-mpnet-base-dot-v1}) and merges results using Reciprocal Rank Fusion (RRF).
    \item[AI Provider Gateway:] Abstracted client supporting Anthropic, OpenAI, XAI, and MiniMax with dynamic per-pipeline configurations.
    \item[Zoom Pipeline:] Captures webhooks, downloads transcripts using refreshed OAuth tokens, parses VTT files, and outputs to review insights and auto-approved knowledge bases.
    \item[Moderation \& Reputation:] Tracks Spurti Points, issues warnings, logs bans, and handles user account anonymization.
\end{description}

\section{Feature Spotlight}
\subsection{Zoom Ingestion with OAuth (Demo Duration: 15s)}
Allows lecturers or hosts to connect their Zoom accounts via OAuth. When a session ends, the recording transcript is automatically parsed and converted into search-ready vector documents.
\subsection{AI Auto-Answer Pipeline (Demo Duration: 15s)}
Unanswered forum posts are checked against the knowledge bases. Answers with high confidence ($\ge 0.85$) are auto-posted, reducing queue times.
\subsection{FAQ Audit \& Freshness (Demo Duration: 15s)}
FAQs are checked for correctness against new materials. Expired FAQs enter a peer-review voting system to be verified or escalated.
\subsection{Golden Ticket Spurti Points Escalation (Demo Duration: 15s)}
Allows students to spend earned SP points to push urgent tickets to the top of the admin queue, restricted by a 48h cooldown.

\section{Challenges \& Limitations}
\begin{itemize}
    \item \textbf{Resource Consumption:} Local embedding generation is resource-intensive for high-concurrency environments.
    \item \textbf{OAuth Race Conditions:} Parallel webhooks can trigger simultaneous Zoom token refreshes. A locking cache was introduced to resolve this.
    \item \textbf{Unwired Freshness Cron:} The freshness pipeline cron job is coded but requires manual trigger setup or wiring to a scheduler in \texttt{server.ts}.
\end{itemize}

\section{Future Enhancements}
\begin{itemize}
    \item Implement BullMQ for robust backend job queue scheduling.
    \item Create Slack and Discord search bots.
    \item Transition event streams to full-duplex WebSockets.
    \item Build a multi-tenant batch management layout.
\end{itemize}

\section{Conclusion}
Shamagama shows that FAQ systems do not need to be static. By coupling hybrid vector search with automated Zoom ingestion, LLM auditing, and reputation-driven community escalation, the platform ensures that knowledge is captured, curated, and kept accurate.

\end{document}
